\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\title{}

\begin{document}

\maketitle

\section{Introduction to fluids and related concepts}
\subsection{Element, fluids}
\subsubsection{Definitions}
In general, a ‘fluid’ is a special kind of continuum. A continuum is a collection of particles so numerous that the dynamics of individual particles cannot be followed, leaving only a description of the collection in terms of ‘average’ or ‘bulk’ quantities: number of particles per unit volume, density of energy, density of momentum, pressure, temperature, etc. The behavior of a lake of water, and the gravitational field it generates, does not depend upon where any one particular water molecule happens to be: it depends only on the average properties of huge collections of molecules.

These properties can vary from point to point in the lake: the pressure is larger at the bottom than at the top, and the temperature may vary as well. The atmo-sphere, another fluid, has a density that varies with position. This raises the question of how large a collection of particles to average over: it must clearly be large enough so that the individual particles don’t matter, but it must be small enough so that it is relatively homogeneous: the average velocity, kinetic energy, and interparticle spacing must be the same everywhere in the collection. Such a collection is called an ‘element’.

\subsubsection{Properties of fluid}

So far, this notion of a continuum embraces rocks as well as gases. A fluid is a continuum that ‘flows’: this definition is not very precise, and so the division between solids and fluids is not very well defined. Most solids will flow under high enough pressure. What makes a substance rigid? After some thought we should be able to see that rigidity comes from forces parallel to the interface between two elements. Two adjacent elements can push and pull on each other, but the continuum won’t be rigid unless they can also prevent each other from sliding along their common boundary. A fluid is characterized by the weakness of such antislipping forces compared to the direct push–pull force, which is called pressure.
\subsection{Perfect fluid, dust}
\subsubsection{Perfect fluid}
A perfect fluid is defined as one in which all anti slipping forces are zero, and the only force between neighboring fluid elements is pressure
\subsubsection{Dust}
We will introduce the relativistic description of a fluid with the simplest one: ‘dust’ is defined to be a collection of particameles, all of which are at rest in some one Lorentz frame (MCRF)

$ n := $  number density in the MCRF of the element.
\\
$\frac{n}{\sqrt{1-v^2}} = $ number density in frame in which particles have velocity $v$. 
\subsection{The number-flux four-vector.}

\subsubsection{A unification of number density and flux in a four-vertor form.}

Consider the vector N defined by:
$$ \vec{N} = n \vec{U}$$
with:
\begin{eqnarray*}
 \vec{U}_{\vec{O}} ( \frac{1}{\sqrt{1-v^2}},\frac{v^x}{\sqrt{1-v^2}},\frac{v^y}{\sqrt{1-v^2}},\frac{v^z}{\sqrt{1-v^2}} )
 \end{eqnarray*}
It follows that
\begin{eqnarray*}
 \vec{N}_{\vec{O}} ( \frac{n}{\sqrt{1-v^2}},\frac{n v^x}{\sqrt{1-v^2}},\frac{n v^y}{\sqrt{1-v^2}},\frac{n v^z}{\sqrt{1-v^2}} ) 
\end{eqnarray*}
in the Lorentz non rest Frame;\\
Finally we have:
$$ \vec{N} \dot \vec{N} = -n^2 , n = (-\vec{N} \dot \vec{N})^{1/2}. $$
\subsubsection{The flux across the surface}
The definition of flux: the flux of particles across a surface is the number crossing a unit area of that surface in a unit time. This clearly depends on the inertial reference frame (‘area’) and ‘time’ are frame-dependent concepts) and on the orientation of the surface (a surface parallel to the velocity of the particles won’t be crossed by any of them)

Before going on to discuss other properties of fluids, we should mention a useful fact. An inertial frame, which up to now has been defined by its four-velocity, can be defined also by a one-form, namely that associated with its four-velocity g( U, ). This has components
$$ U_\alpha = \eta_{\alpha \beta} U^\beta$$
or, in this frame,
$$ U_0 = -1, U_i = 0 $$
For instance, the energy of a particle whose four-momentum
is $\vec{p}$ is
$$ E = \langle dt, \vec{p} \rangle = p^0. $$

$$ E = -\vec{p} \dot \vec{U}. $$

\section{Cái gì đó}
\section{Cái gì đó 2}
\section{Stress-energy in General Relavity}
\subsection{Energy conditions and demonstrations}
\subsubsection{The four energy conditions and their physical meaning}
$ \textbf{Null energy condition}$\\
The null energy condition stipulates that for every future-pointing null vector field $\vec{k}$\\
${\displaystyle \rho =T_{ab}k^{a}k^{b}\geq 0.}$ \\
\\
$ \textbf{Weak energy condition}$\\
The weak energy condition stipulates that for every timelike vector field {\displaystyle {\vec {X}},} {\displaystyle {\vec {X}},} the matter density observed by the corresponding observers is always non-negative:\\
${\displaystyle \rho =T_{ab}X^{a}X^{b}\geq 0.}$
\\
\\
$ \textbf{Dominant energy condition}$\\
The dominant energy condition stipulates that, in addition to the weak energy condition holding true, for every future-pointing causal vector field (either timelike or null) {\displaystyle {\vec {Y}},} {\displaystyle {\vec {Y}},} the vector field {\displaystyle -{T^{a}}_{b}Y^{b}} {\displaystyle -{T^{a}}_{b}Y^{b}} must be a future-pointing causal vector. That is, mass–energy can never be observed to be flowing faster than light.\\
\\
$ \textbf{Strong energy condition}$\\
The strong energy condition stipulates that for every timelike vector field {\displaystyle {\vec {X}}} {\vec {X}}, the trace of the tidal tensor measured by the corresponding observers is always non-negative:\\
${\displaystyle \left(T_{ab}-{\frac {1}{2}} T g_{ab}\right)X^{a}X^{b}\geq 0}$ \\
\subsubsection{Applications to perfect fluid}
$$ {\displaystyle T^{ab}=\rho u^{a}u^{b}+p h^{ab},} $$
\\
where ${\displaystyle {\vec {u}}} {\vec {u}}$ is the four-velocity of the matter particles and where ${\displaystyle h^{ab}\equiv g^{ab}+u^{a}u^{b}} h^{{ab}}\equiv g^{{ab}}+u^{{a}}u^{{b}}$ is the projection tensor onto the spatial hyperplane elements orthogonal to the four-velocity, at each event. (Notice that these hyperplane elements will not form a spatial hyperslice unless the velocity is vorticity-free; that is, irrotational.) With respect to a frame aligned with the motion of the matter particles, the components of the matter tensor take the diagonal form
\\
\begin{equation}
    {\displaystyle T^{{\hat {a}}{\hat {b}}}= {\begin{matrix} \rho &0&0&0\\0&p&0&0\\0&0&p&0\\0&0&0&p \end{matrix}}.} 
\end{equation}  
\\
Here, ${\displaystyle \rho } $ is the energy density and ${\displaystyle p} $ is the pressure.
\\
The energy conditions can then be reformulated in terms of these eigenvalues:
\\
\\
- The null energy condition stipulates that ${\displaystyle \rho +p\geq 0.} {\displaystyle \rho +p\geq 0.}$\\
- The weak energy condition stipulates that ${\displaystyle \rho \geq 0,\;\;\rho +p\geq 0.} {\displaystyle \rho \geq 0,\;\;\rho +p\geq 0.}$
\\
- The dominant energy condition stipulates that ${\displaystyle \rho \geq |p|.} {\displaystyle \rho \geq |p|.}$
\\
- The strong energy condition stipulates that ${\displaystyle \rho +p\geq 0,\;\;\rho +3p\geq 0.} {\displaystyle \rho +p\geq 0,\;\;\rho +3p\geq 0.}$
\\
\\
The implications among these conditions are indicated in the figure at right. Note that some of these conditions allow negative pressure. Also, note that despite the names the strong energy condition does not imply the weak energy condition even in the context of perfect fluids.
\end{document}
